Tropical Andes montane and lowland forest bird and mammal species GBIF

### 2023-07-30 code/L0/L0_TropicalAndes_frugivores_GBIF.Rmd

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0154158-230224095556074", path = output_path) %>%
  occ_download_import()
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropAndes_GBIF_frugivore_occ_species.csv") 
write.csv(GBIF_occ_SpeciesList, file = TropicalAndes_GBIF_path)
```

>>>>

# Retrive GBIF download, save file, and load into r
```{r}
d <- occ_download_get("0154158-230224095556074", path = output_path, overwrite = TRUE) %>%
  occ_download_import()
```

@@

# Write data to csv
```{r}
TropicalAndes_GBIF_path <- file.path(output_path,"TropicalAndes_GBIF_frugivore_occ.csv") 
write.csv(d, file = TropicalAndes_GBIF_path)
TropicalAndes_GBIF_species_path <- file.path(output_path,"TropicalAndes_GBIF_frugivore_occ_species.csv") 
write.csv(GBIF_occ_SpeciesList, file = TropicalAndes_GBIF_path)
```
